AtmoSwing (v1.4): Analogue Technique Model for Statistical weather forecastING

### 2016-02-05 AtmoSwing - Geoscientific Model Development/template.tex
Update of the Copernicus Linux package.

%% 2-Column Papers and Discussion Papers
%\documentclass[gmd, manuscript]{copernicus}
\documentclass[gmd]{copernicus}

@@

The purpose of this paper is not to argue in favour or against this approach, which has proved to be used efficiently either in operational forecasting or more recently in climate studies \citep{Dayon2015}. \citet{Bliefernicht2010} compared the performance of the AM with a forecasting method based on a weather types approach, and concluded that the AM was more efficient.

>>>>

%% 2-Column Papers and Discussion Papers
\documentclass[gmd, manuscript]{copernicus}
%\documentclass[gmd]{copernicus}

@@

The purpose of this paper is not to argue in favour or against this approach, which has proved to be used efficiently either in operational forecasting \citep{Djerboua2001} or more recently in climate studies \citep{Dayon2015}. \citet{Bliefernicht2010} compared the performance of the AM with a forecasting method based on a weather types approach, and concluded that the AM was more efficient.
